Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-01-27 paper.tex
update fig, fix caption

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Enrichment Cascade Alternatives under JCPOA}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\begin{table}[htb]
\centering
  \caption{Summary of cascade properties for each level}
\begin{tabular}{cllll}
\toprule

@@

\subsubsection{Recycling tails}
When recycling the tails from the each cascade level, both cases behave
the same way. As the tails have an higher enrichment than the product they are
blended to, recycling the tails has bumps up the enrichment of the
product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modeling potential JCPOA diversion scenarios with Cyclus}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\begin{table}[htb]
\centering
  \caption{Summary of cascade properties for each level.}
\begin{tabular}{cllll}
\toprule

@@

\subsubsection{With tail recycling}
When recycling the tails from the each cascade level, both cases behave
the same way. As the tails have an higher enrichment than the product they are
blended to, recycling the tails has bumps up the enrichment of the
product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).
